When are Fuzzy Extractors Possible?

### 2014-10-06 trunk/info-bounds/FuzzyExtPossibility.tex
adam's edits on distribution-aware prior work; leo's edits to def of Hfuzz preamble

This characterization justifies $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  better than cruder measures such as $\Hoo(W)-\log |B_t|$.

@@

\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have roughly the same probability.  We call distributions of this type ``nearly flat.''  Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguiate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the size of hash output space is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is nearly flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

@@

\subsection{Sufficiency of $\Hfuzz(W)$ in related settings}
\label{sec:related settings}
The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.   In this computational setting, fuzzy extractors and secure sketches can be constructed for the family of all distributions $W$ with superlogarithmic $\Hfuzz$ by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}. The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.  In addition to relying on strong assumptions for security (namely, the existence of semantically-secure multilinear maps), this construction is not of practical efficiency. Note that if this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).

@@

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:known distributions}, we construct a fuzzy extractor for every known distribution with fuzzy min-entropy.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results for secure sketches and fuzzy extractors for families of distributions respectively.

@@

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $w$} is the set of all points within radius $t$, that is, $B_t(w) = \{w'| \dis(w, w')\leq t\}$.  If the size of a ball in a metric space does not depend on $w$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(w,w') = \{i | w_i \neq w'_i\}$ where $\mathcal{Z}$ is some alphabet.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_\kappa$ denotes the uniformly  distributed random variable on $\{0,1\}^\kappa$.  Throughout this work, we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.

\subsection{Fuzzy Extractors for families of distributions}\label{sec:fuzz extractor}

@@

\subsection{Fuzzy min-entropy: a necessary condition}
\label{sec:minimal conditions}

In an ideal world, $p$ is not useful to an adversary.  The adversary's only attack method is to execute $\rep(\cdot, p)$ on different $w'$.  In this world, $\rep$ outputs $\key$ if the input is close enough and provides no other  information.  The security of a fuzzy extractor in this world is the maximum weight of $W$ inside a ball of radius $t$:

>>>>

A number of previous works in this known-distribution setting have provided efficient algorithms and
tight bounds for specific distributions---generally the uniform distribution or
i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
Our characterization may be seen as unifying previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.

@@

\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have the same probability (so-called ``flat'' distributions).   Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the size of hash output space is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

@@

\subsection{Sufficiency of $\Hfuzz$ in Related Settings}
\label{sec:related settings}
The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.   In this computational setting, fuzzy extractors and secure sketches can be constructed for the family of all distributions $W$ with superlogarithmic $\Hfuzz$ by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}. The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.  In addition to relying on strong assumptions for security (namely, the existence of semantically-secure multilinear maps), this construction is not of practical efficiency. Note that if this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).

@@

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:known distributions}, we construct a fuzzy extractor for every known distribution with fuzzy min-entropy.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results  for families of distributions for secure sketches and fuzzy extractors, respectively.

@@

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $w$} is the set of all points within radius $t$, that is, $B_t(w) = \{w'| \dis(w, w')\leq t\}$.  If the size of a ball in a metric space does not depend on $w$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(w,w') = \{i | w_i \neq w'_i\}$ where $\mathcal{Z}$ is some alphabet.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_\kappa$ denotes the uniformly  distributed random variable on $\{0,1\}^\kappa$.  Throughout this work, we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience. A \emph{negligible} function $\ngl(n)$ is one that decreases faster than any positive inverse polynomial as $n\rightarrow \infty$.

\subsection{Fuzzy Extractors for Families of Distributions}\label{sec:fuzz extractor}

@@

\subsection{Fuzzy min-entropy: a Necessary Condition}
\label{sec:minimal conditions}
The value $p$ allows everyone, including the adversary, to find the output of $\rep(\cdot, p)$ on any input $w'$. Ideally,  $p$ should not provide any useful information beyond this ability, and the outputs of $\rep$ on inputs that are too distant from $w$ should provide no useful information, either.  In this ideal scenario, the adversary is limited to trying to guess a $w'$ that is $t$-close to $w$. 
Letting $w'$ be the center of the maximum-weight ball in $W$ would be optimal for the adversary.
We therefore measure the quality of a source by (the negative logarithm of) this weight.
